---
title: "My Shiny Application"
author: "Daniel Ludewig"
date: "31 October 2017"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE, cache = TRUE)
```

## Healthy Life Expectancy in Scotland

I have developed an app that takes historical Healthy Life Expectancy (HLE) rates for men and women and displays them on a plot. 

It also allows the user to select the range of years displayed, fits a linear model and predicts future or past HLEs. 

## What is Healthy Life Expectancy?

According to the [data source](http://statistics.gov.scot/data/healthy-life-expectancy), HLE is:

> HLE is an estimate of how long the average person might be expected to live in a 'healthy' state.

It differs from Life Expectancy, which is more plainly estimate of how many years a person might be expected to live. 

It is a key summary of a populations health. 

## Displaying the Data

The plot below, is an example of a plot displayed by the app. 

```{r plot}
suppressPackageStartupMessages(library(dplyr))
all_data <- read.csv("https://danielludewig.github.io/Data_Products/test_data.csv", 
                 header = TRUE)
data <- filter(all_data, (Confidence.Interval == "All")&(DateCode < 2009))
with(data, plot(x=DateCode, y= Value, type = "n"))
with(data[which(data$Gender=="Male"),],points(x=DateCode, y=Value, pch=20, col="steelblue"))
with(data[which(data$Gender=="Female"),],points(x=DateCode, y=Value,pch=20, col="coral"))  
```

## Predictions

The **Predictions** tab takes the information entered by the user on the side panel, fits a linear model, and predicts the HLE for the year stipulated by the user. 

It will also display the relevant statistical information associated with the model. 

Thanks for reading. 


